%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.1.5, 1 December 2018) written by
% LianTze Lim (liantze@gmail.com), based on the
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

\documentclass[10pt,a4paper,ragged2e]{altacv}

% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

\usepackage{hyperref}

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{Black}{HTML}{000000}
\colorlet{heading}{Black}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{\href{https://nnischal.me}{Nischal Neupane}}
\tagline{Machine Learning Engineer}
\personalinfo{
  \linkedin{\href{https://www.linkedin.com/in/nneupane2/}{nneupane2}}
  \email{\href{mailto:neupanenischal1@gmail.com}{neupanenischal1@gmail.com}} 
  \github{\href{https://github.com/lulrai}{lulrai}}
  \phone{\href{tel:+310684880710}{(+31) 068 488 0710}}
  \location{Enschede, Netherlands}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}\makecvheader
\end{fullwidth}

\AtBeginEnvironment{itemize}{\small}

\cvsection[resume\_sidebar]{Experience}

\cvevent{Machine Learning - Graduate Intern}{\href{https://www.asml.com/en}{ASML}}{April 2023 -- October 2023}{Veldhoven, Netherlands}
\begin{itemize}
    \item Utilized KNIME and Azure Databricks for data processing and model training to predict a next-error event with over 90\% accuracy using a Transformer model.
    \item Found validated root causes of an error event through the use of Layerwise Relevance Propogation to understand the relevance of the input data.
\end{itemize}

\divider

\cvevent{Software Engineering Assistant}{\href{https://www.asml.com/en}{DEMCON Convergence}}{Feb 2022 -- Feb 2023}{Enschede, Netherlands}
\begin{itemize}
    \item Developed frontend and backend software for embedded systems in microfluidics using QML, C++, and JavaScript.
    \item Created unit tests and hardware tests to ensure a seamless and intuitive user experience.
\end{itemize}

\divider

\cvevent{Junior Data Scientist}{\href{https://www.buckle.com}{The Buckle Inc.}}{Aug 2020 -- Jun 2021}{Omaha, Nebraska, USA}
\begin{itemize}
\item Implemented a pre-trained "word2vec" machine learning model for product recommendations and for big data integration within the checkout system.
\item Performed A/B testing on the recommendations generated by the implemented models.
\end{itemize}

\divider

\cvevent{Software Developer Intern}{\href{https://www.wecare-insurance.com/contact/}{WeCare Insurance}}{Aug 2020 -- May 2021}{Omaha, Nebraska, USA}
\begin{itemize}
\item Scraped insurance policy data from HTML forms using Java and Selenium.
\item Stored parsed data in a SQL database and relayed it to other clients asynchronously.
\end{itemize}

\cvsection{Project}

\cvevent{\href{https://github.com/lulrai/bot-client}{\github{LoTRO Data Extractor}}}{}{}{}
\begin{itemize}
\item Developed a character tracking system for the MMORPG game "Lord of the Rings Online" using Python and Pymem library with asynchronous syncing of the game data with a MongoDB database and discord bot, creating a seamless user experience.
\item Reverse-engineered the game client using HexRays IDA and HexEdit to retrieve memory pointers containing useful assets and data.
\end{itemize}

\divider

\cvevent{\href{https://github.com/lulrai/bot-client}{\github{Cubic Bot}}}{}{}{}
\begin{itemize}
\item Developed a Discord bot written in Java using Maven framework that integrates with the internal servers of the game Cubic Castles to provide real-time information about the game, such as crafting and item searching.
\item Utilized API calls and parse the response data to provide accurate and up-to-date information to the users and deployed the bot on GCS to ensure seamless performance and accessibility to users.
\end{itemize}

\clearpage

% \cvsection[page2sidebar]{Publications}
% 
% \nocite{*}
% 
% \printbibliography[heading=pubtype,title={\printinfo{\faBook}{Books}},type=book]
% 
% \divider
% 
% \printbibliography[heading=pubtype,title={\printinfo{\faFileTextO}{Journal Articles}}, type=article]
% 
% \divider
% 
% \printbibliography[heading=pubtype,title={\printinfo{\faGroup}{Conference Proceedings}},type=inproceedings]
% 
%% If the NEXT page doesn't start with a \cvsection but you'd
%% still like to add a sidebar, then use this command on THIS
%% page to add it. The optional argument lets you pull up the
%% sidebar a bit so that it looks aligned with the top of the
%% main column.
% \addnextpagesidebar[-1ex]{page3sidebar}


\end{document}
